Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
Update
made timing diagram larger and changed section name from "Conclusion" -> "Conclusions"

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth]{images/timingER3.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with proposed improvements with loss of a) Single packet b) Two packets c) Single packet and probe loss}\label{timingNew}
\end{figure}

@@

Results comparing the burst completion time for new MPTCP TLP with that of TCP and MPTCP TLP for the considered cases are provided in 
Figure~\ref{mpnew}. In Figure~\ref{1pn}, MPTCP-New performs better than TCP in all scenarios, performs equal to MPTCP in symmetric scenarios and 
performs better than MPTCP in asymmetric scenarios with a lower delay on the alternate path. This improvement is for the reason that MPTCP-New 
allows the packet to be retransmitted on the alternate path much before the RTO. In two packet tail loss scenario as in Figure~\ref{2pn}, MPTCP-New
performs better than TCP in all scenarios and better than MPTCP in all scenarios except when the alternate path has a significantly higher delay 
than the original path, where performance is the same. In the single packet together with probe loss scenario as in Figure~\ref{1ppn}, MPTCP-New 
performs better than both MPTCP and TCP in all scenarios with PTO triggering the probe retransmission on alternate path much earlier than the RTO.

%\kern-1em
\section{Conclusion}\label{conc}
This paper provides a short comparative analysis of retransmission behavior with TCP and MPTCP protocols using various loss patterns for tail loss.
The three cases of tail loss together with deterministic loss patterns allow us to dissect the retransmission behavior at packet level to 
understand possible improvements.
We propose a less conservative approach to trigger retransmission on an alternate path in the event of tail loss probe timeout, which otherwise 
triggered with an RTO. Our emulation experiments  using a modified Linux implementation, show that the proposed approach in fact improves the 
burst completion time in most cases and equals the existing implementation in other cases. The proposed approach improves the performance when 
the alternate path has lower delay than the original loss path and the advantage increases with degree of asymmetry between the paths. 
Temporary path failures can cause probe loss along with packet loss. The approach is very effective in case of probe loss which otherwise 
incur RTO timeout to trigger retransmission on either path. However, the latency improvement comes at a cost of additional network traffic 
from the retransmitted packets. This study is limited to emulated synthetic traffic and static drop pattern that serve the purpose of localizing 
the loss events. A comprehensive study covering various traffic types and loss patterns is considered for future investigation. Further, we plan 
to investigate less conservative approaches for other retransmission events.

>>>>

\begin{figure*}
\begin{center}
    \includegraphics[angle=0, width=0.8\textwidth]{images/timingER3NewTLP1}
\end{center}
\caption{Timing diagram of MPTCP behavior with proposed improvements with loss of a) Single packet b) Two packets c) Single packet and probe loss}\label{timingNew}
\end{figure*}

@@

@@

Results comparing the burst completion time for new MPTCP TLP with that of TCP and MPTCP TLP for the considered cases are provided in 
Figure~\ref{mpnew}. In Figure~\ref{1pn}, MPTCP-New performs better than TCP in all scenarios, performs equal to MPTCP in symmetric scenarios and 
performs better than MPTCP in asymmetric scenarios with a lower delay on the alternate path. MPTCP-New achieves this improvement by retransmitting
 lost packets on the alternate path much before the RTO. In two packet tail loss scenario as in Figure~\ref{2pn}, MPTCP-New
performs better than TCP in all scenarios and better than MPTCP in all scenarios except when the alternate path has a significantly higher delay 
than the original path, where performance is the same. In the single packet together with probe loss scenario as in Figure~\ref{1ppn}, MPTCP-New 
performs better than both MPTCP and TCP in all scenarios with PTO triggering the probe retransmission on alternate path much earlier than the RTO.

%\kern-1em
\section{Conclusions}\label{conc}
This paper provides a short comparative analysis of retransmission behavior with TCP and MPTCP protocols using various loss patterns for tail loss.
The three cases of tail loss together with deterministic loss patterns allow us to dissect the retransmission behavior at packet level to 
understand possible improvements.
We propose a less conservative approach to trigger retransmission on an alternate path in the event of tail loss probe timeout, which otherwise 
triggered with an RTO. Our emulation experiments  using a modified Linux implementation, show that the proposed approach in fact improves the 
burst completion time in most cases and equals the existing implementation in other cases. The proposed approach improves the performance when 
the alternate path has lower delay than the original loss path and the advantage increases with degree of asymmetry between the paths. 
Temporary path failures can cause probe loss along with packet loss. The approach is very effective in case of probe loss which otherwise 
incur RTO timeout to trigger retransmission on either path. However, the latency improvement comes at a cost of additional network traffic 
from the retransmitted packets. This study is limited to emulated synthetic traffic and static drop pattern that serve the purpose of localizing 
the loss events. A comprehensive study covering various traffic types and loss patterns is considered for future investigation. Further, we plan 
to investigate less conservative approaches for other retransmission events.
